\documentclass{book}
\usepackage{customstyle} % Include the custom style sheet
\usepackage{imakeidx} % Include the imakeidx package for creating index

% Create an index
\makeindex

\begin{document}

\tableofcontents % Add table of contents

\chapter{Introduction}
This is the introduction.

% Include Chapter 1.tex with no page break
\input{chapter1}

% Include Chapter2.tex with a page break
\include{chapter2}
% Your document content goes here...

% Print the bibliography
\bibliography{references} % Specify the .bib file name without the extension

% Include index
\printindex

\appendix

\chapter{Notes }


\section{The Meaning of The tribe of Dan}

The KJV translates Strong's H1777 in the following manner: judge (18x), plead the cause (2x), contend (1x), execute (1x), plead (1x), strife (1x).
Gen 6:3 KJV - 3 And the LORD said, My spirit shall not always strive[H1777] with man, for that he also [is] flesh: yet his days shall be an hundred and twenty years.
Gen 15:14 KJV - 14 And also that nation, whom they shall serve, will I judge:[H1777] and afterward shall they come out with great substance.
Gen 30:6 KJV - 6 And Rachel said, God hath judged[H1777] me, and hath also heard my voice, and hath given me a son: therefore called she his name Dan.
Gen 49:16 KJV - 16 Dan shall judge[H1777] his people, as one of the tribes of Israel.
Deu 32:36 KJV - 36 For the LORD shall judge[H1777] his people, and repent himself for his servants, when he seeth that [their] power is gone, and [there is] none shut up, or left.
1Sa 2:10 KJV - 10 The adversaries of the LORD shall be broken to pieces; out of heaven shall he thunder upon them: the LORD shall judge[H1777] the ends of the earth; and he shall give strength unto his king, and exalt the horn of his anointed.
2Sa 19:9 KJV - 9 And all the people were at strife[H1777] throughout all the tribes of Israel, saying, The king saved us out of the hand of our enemies, and he delivered us out of the hand of the Philistines; and now he is fled out of the land for Absalom.
Job 36:31 KJV - 31 For by them judgeth[H1777] he the people; he giveth meat in abundance.
Psa 7:8 KJV - 8 The LORD shall judge[H1777] the people: judge me, O LORD, according to my righteousness, and according to mine integrity [that is] in me.
Psa 9:8 KJV - 8 And he shall judge the world in righteousness, he shall minister judgment[H1777] to the people in uprightness.
Psa 50:4 KJV - 4 He shall call to the heavens from above, and to the earth, that he may judge[H1777] his people.
Psa 54:1 KJV - 1 [[To the chief Musician on Neginoth, Maschil, [A Psalm] of David, when the Ziphims came and said to Saul, Doth not David hide himself with us?]] Save me, O God, by thy name, and judge[H1777] me by thy strength.
Psa 72:2 KJV - 2 He shall judge[H1777] thy people with righteousness, and thy poor with judgment.
Psa 96:10 KJV - 10 Say among the heathen [that] the LORD reigneth: the world also shall be established that it shall not be moved: he shall judge[H1777] the people righteously.
Psa 110:6 KJV - 6 He shall judge[H1777] among the heathen, he shall fill [the places] with the dead bodies; he shall wound the heads over many countries.
Psa 135:14 KJV - 14 For the LORD will judge[H1777] his people, and he will repent himself concerning his servants.
Pro 31:9 KJV - 9 Open thy mouth, judge righteously, and plead[H1777] the cause of the poor and needy.
Ecc 6:10 KJV - 10 That which hath been is named already, and it is known that it [is] man: neither may he contend[H1777] with him that is mightier than he.
Isa 3:13 KJV - 13 The LORD standeth up to plead, and standeth to judge[H1777] the people.
Jer 5:28 KJV - 28 They are waxen fat, they shine: yea, they overpass the deeds of the wicked: they judge[H1777] not the cause, the cause of the fatherless, yet they prosper; and the right of the needy do they not judge.
Jer 21:12 KJV - 12 O house of David, thus saith the LORD; Execute[H1777] judgment in the morning, and deliver [him that is] spoiled out of the hand of the oppressor, lest my fury go out like fire, and burn that none can quench [it], because of the evil of your doings.
Jer 22:16 KJV - 16 He judged[H1777] the cause of the poor and needy; then [it was] well [with him: was] not this to know me? saith the LORD.
Jer 30:13 KJV - 13 [There is] none to plead[H1777] thy cause, that thou mayest be bound up: thou hast no healing medicines.
Zec 3:7 KJV - 7 Thus saith the LORD of hosts; If thou wilt walk in my ways, and if thou wilt keep my charge, then thou shalt also judge[H1777] my house, and shalt also keep my courts, and I will give thee places to walk among these that stand by.

\chapter{meanings of Benjamin or Ben}

bane; from H1129; a son (as a builder of the family name), in the widest sense (of literal and figurative relationship, including grandson, subject, nation, quality or condition, etc., (like father or brother), etc.):—afflicted, age, (Ahoh-) (Ammon-) (Hachmon-) (Lev-) ite, (anoint-) ed one, appointed to, (+) arrow, (Assyr-) (Babylon-) (Egypt-) (Grec-) ian, one born, bough, branch, breed, + (young) bullock, + (young) calf, × came up in, child, colt, × common, × corn, daughter, × of first, firstborn, foal, + very fruitful, + postage, × in, + kid, + lamb, (+) man, meet, + mighty, + nephew, old, (+) people, rebel, + robber, × servant born, × soldier, son, + spark, steward, + stranger, × surely, them of, + tumultuous one, valiant(-est), whelp, worthy, young (one), youth.

\section{}
Gen 3:16 KJV
Unto the woman he said, I will greatly multiply thy sorrow and thy conception; in sorrow thou shalt bring forth children;[H1121] and thy desire [shall be] to thy husband, and he shall rule over thee.

Gen 4:17 KJV
And Cain knew his wife; and she conceived, and bare Enoch: and he builded a city, and called the name of the city, after the name of his son,[H1121] Enoch.

Gen 4:25 KJV
And Adam knew his wife again; and she bare a son,[H1121] and called his name Seth: For God, [said she], hath appointed me another seed instead of Abel, whom Cain slew.

Gen 4:26 KJV
And to Seth, to him also there was born a son;[H1121] and he called his name Enos: then began men to call upon the name of the LORD.

Gen 5:4 KJV
And the days of Adam after he had begotten Seth were eight hundred years: and he begat sons[H1121] and daughters:

Gen 5:7 KJV
And Seth lived after he begat Enos eight hundred and seven years, and begat sons[H1121] and daughters:

Gen 5:10 KJV
And Enos lived after he begat Cainan eight hundred and fifteen years, and begat sons[H1121] and daughters:

Gen 5:13 KJV
And Cainan lived after he begat Mahalaleel eight hundred and forty years, and begat sons[H1121] and daughters:

Gen 5:16 KJV
And Mahalaleel lived after he begat Jared eight hundred and thirty years, and begat sons[H1121] and daughters:

Gen 5:19 KJV
And Jared lived after he begat Enoch eight hundred years, and begat sons[H1121] and daughters:

Gen 5:22 KJV
And Enoch walked with God after he begat Methuselah three hundred years, and begat sons[H1121] and daughters:

Gen 5:26 KJV
And Methuselah lived after he begat Lamech seven hundred eighty and two years, and begat sons[H1121] and daughters:

Gen 5:28 KJV
And Lamech lived an hundred eighty and two years, and begat a son:[H1121]

Gen 5:30 KJV
And Lamech lived after he begat Noah five hundred ninety and five years, and begat sons[H1121] and daughters:

Gen 5:32 KJV
And Noah was five hundred years old:[H1121] and Noah begat Shem, Ham, and Japheth.

Gen 6:2 KJV
That the sons[H1121] of God saw the daughters of men that they [were] fair; and they took them wives of all which they chose.

Gen 6:4 KJV
There were giants in the earth in those days; and also after that, when the sons[H1121] of God came in unto the daughters of men, and they bare [children] to them, the same [became] mighty men which [were] of old, men of renown.

Gen 6:10 KJV
And Noah begat three sons,[H1121] Shem, Ham, and Japheth.

Gen 6:18 KJV
But with thee will I establish my covenant; and thou shalt come into the ark, thou, and thy sons,[H1121] and thy wife, and thy sons'[H1121] wives with thee.

Gen 7:6 KJV
And Noah [was] six hundred years old[H1121] when the flood of waters was upon the earth.

Gen 7:7 KJV
And Noah went in, and his sons,[H1121] and his wife, and his sons'[H1121] wives with him, into the ark, because of the waters of the flood.

Gen 7:13 KJV
In the selfsame day entered Noah, and Shem, and Ham, and Japheth, the sons[H1121] of Noah, and Noah's wife, and the three wives of his sons[H1121] with them, into the ark;

Gen 8:16 KJV
Go forth of the ark, thou, and thy wife, and thy sons,[H1121] and thy sons'[H1121] wives with thee.

Gen 8:18 KJV
And Noah went forth, and his sons,[H1121] and his wife, and his sons'[H1121] wives with him:

Gen 9:1 KJV
And God blessed Noah and his sons,[H1121] and said unto them, Be fruitful, and multiply, and replenish the earth.

Gen 9:8 KJV
And God spake unto Noah, and to his sons[H1121] with him, saying,

Gen 9:18 KJV
And the sons[H1121] of Noah, that went forth of the ark, were Shem, and Ham, and Japheth: and Ham [is] the father of Canaan.

Gen 9:19 KJV
These [are] the three sons[H1121] of Noah: and of them was the whole earth overspread.

Gen 9:24 KJV
And Noah awoke from his wine, and knew what his younger son[H1121] had done unto him.

Gen 10:1 KJV
Now these [are] the generations of the sons[H1121] of Noah, Shem, Ham, and Japheth: and unto them were sons[H1121] born after the flood.

Gen 10:2 KJV
The sons[H1121] of Japheth; Gomer, and Magog, and Madai, and Javan, and Tubal, and Meshech, and Tiras.

Gen 10:3 KJV
And the sons[H1121] of Gomer; Ashkenaz, and Riphath, and Togarmah.

Gen 10:4 KJV
And the sons[H1121] of Javan; Elishah, and Tarshish, Kittim, and Dodanim.

Gen 10:6 KJV
And the sons[H1121] of Ham; Cush, and Mizraim, and Phut, and Canaan.

Gen 10:7 KJV
And the sons[H1121] of Cush; Seba, and Havilah, and Sabtah, and Raamah, and Sabtecha: and the sons[H1121] of Raamah; Sheba, and Dedan.

Gen 10:20 KJV
These [are] the sons[H1121] of Ham, after their families, after their tongues, in their countries, [and] in their nations.

Gen 10:21 KJV
Unto Shem also, the father of all the children[H1121] of Eber, the brother of Japheth the elder, even to him were [children] born.

Gen 10:22 KJV
The children[H1121] of Shem; Elam, and Asshur, and Arphaxad, and Lud, and Aram.

Gen 10:23 KJV
And the children[H1121] of Aram; Uz, and Hul, and Gether, and Mash.

Gen 10:25 KJV
And unto Eber were born two sons:[H1121] the name of one [was] Peleg; for in his days was the earth divided; and his brother's name [was] Joktan.

Gen 10:29 KJV
And Ophir, and Havilah, and Jobab: all these [were] the sons[H1121] of Joktan.

Gen 10:31 KJV
These [are] the sons[H1121] of Shem, after their families, after their tongues, in their lands, after their nations.

Gen 10:32 KJV
These [are] the families of the sons[H1121] of Noah, after their generations, in their nations: and by these were the nations divided in the earth after the flood.

Gen 11:5 KJV
And the LORD came down to see the city and the tower, which the children[H1121] of men builded.

Gen 11:10 KJV
These [are] the generations of Shem: Shem [was] an hundred years old,[H1121] and begat Arphaxad two years after the flood:

Gen 11:11 KJV
And Shem lived after he begat Arphaxad five hundred years, and begat sons[H1121] and daughters.

Gen 11:13 KJV
And Arphaxad lived after he begat Salah four hundred and three years, and begat sons[H1121] and daughters.

Gen 11:15 KJV
And Salah lived after he begat Eber four hundred and three years, and begat sons[H1121] and daughters.

Gen 11:17 KJV
And Eber lived after he begat Peleg four hundred and thirty years, and begat sons[H1121] and daughters.

Gen 11:19 KJV
And Peleg lived after he begat Reu two hundred and nine years, and begat sons[H1121] and daughters.

\chapter{Roots of Zerubbabel}

zârab, zaw-rab'; a primitive root; to flow away:—wax warm.

\section{}
Gen 10:10 KJV
And the beginning of his kingdom was Babel,[H894] and Erech, and Accad, and Calneh, in the land of Shinar.

Gen 11:9 KJV
Therefore is the name of it called Babel;[H894] because the LORD did there confound the language of all the earth: and from thence did the LORD scatter them abroad upon the face of all the earth.

2Ki 17:24 KJV
And the king of Assyria brought [men] from Babylon,[H894] and from Cuthah, and from Ava, and from Hamath, and from Sepharvaim, and placed [them] in the cities of Samaria instead of the children of Israel: and they possessed Samaria, and dwelt in the cities thereof.

2Ki 17:30 KJV
And the men of Babylon[H894] made Succothbenoth, and the men of Cuth made Nergal, and the men of Hamath made Ashima,

2Ki 20:12 KJV
At that time Berodachbaladan, the son of Baladan, king of Babylon,[H894] sent letters and a present unto Hezekiah: for he had heard that Hezekiah had been sick.

2Ki 20:14 KJV
Then came Isaiah the prophet unto king Hezekiah, and said unto him, What said these men? and from whence came they unto thee? And Hezekiah said, They are come from a far country, [even] from Babylon.[H894]

2Ki 20:17 KJV
Behold, the days come, that all that [is] in thine house, and that which thy fathers have laid up in store unto this day, shall be carried into Babylon:[H894] nothing shall be left, saith the LORD.

2Ki 20:18 KJV
And of thy sons that shall issue from thee, which thou shalt beget, shall they take away; and they shall be eunuchs in the palace of the king of Babylon.[H894]

2Ki 24:1 KJV
In his days Nebuchadnezzar king of Babylon[H894] came up, and Jehoiakim became his servant three years: then he turned and rebelled against him.

2Ki 24:7 KJV
And the king of Egypt came not again any more out of his land: for the king of Babylon[H894] had taken from the river of Egypt unto the river Euphrates all that pertained to the king of Egypt.

2Ki 24:10 KJV
At that time the servants of Nebuchadnezzar king of Babylon[H894] came up against Jerusalem, and the city was besieged.

2Ki 24:11 KJV
And Nebuchadnezzar king of Babylon[H894] came against the city, and his servants did besiege it.

2Ki 24:12 KJV
And Jehoiachin the king of Judah went out to the king of Babylon,[H894] he, and his mother, and his servants, and his princes, and his officers: and the king of Babylon[H894] took him in the eighth year of his reign.

2Ki 24:15 KJV
And he carried away Jehoiachin to Babylon,[H894] and the king's mother, and the king's wives, and his officers, and the mighty of the land, [those] carried he into captivity from Jerusalem to Babylon.[H894]

2Ki 24:16 KJV
And all the men of might, [even] seven thousand, and craftsmen and smiths a thousand, all [that were] strong [and] apt for war, even them the king of Babylon[H894] brought captive to Babylon.[H894]

2Ki 24:17 KJV
And the king of Babylon[H894] made Mattaniah his father's brother king in his stead, and changed his name to Zedekiah.

2Ki 24:20 KJV
For through the anger of the LORD it came to pass in Jerusalem and Judah, until he had cast them out from his presence, that Zedekiah rebelled against the king of Babylon.[H894]

2Ki 25:1 KJV
And it came to pass in the ninth year of his reign, in the tenth month, in the tenth [day] of the month, [that] Nebuchadnezzar king of Babylon[H894] came, he, and all his host, against Jerusalem, and pitched against it; and they built forts against it round about.

2Ki 25:6 KJV
So they took the king, and brought him up to the king of Babylon[H894] to Riblah; and they gave judgment upon him.

2Ki 25:7 KJV
And they slew the sons of Zedekiah before his eyes, and put out the eyes of Zedekiah, and bound him with fetters of brass, and carried him to Babylon.[H894]

2Ki 25:8 KJV
And in the fifth month, on the seventh [day] of the month, which [is] the nineteenth year of king Nebuchadnezzar king of Babylon,[H894] came Nebuzaradan, captain of the guard, a servant of the king of Babylon,[H894] unto Jerusalem:

2Ki 25:11 KJV
Now the rest of the people [that were] left in the city, and the fugitives that fell away to the king of Babylon,[H894] with the remnant of the multitude, did Nebuzaradan the captain of the guard carry away.

2Ki 25:13 KJV
And the pillars of brass that [were] in the house of the LORD, and the bases, and the brasen sea that [was] in the house of the LORD, did the Chaldees break in pieces, and carried the brass of them to Babylon.[H894]

2Ki 25:20 KJV
And Nebuzaradan captain of the guard took these, and brought them to the king of Babylon[H894] to Riblah:

2Ki 25:21 KJV
And the king of Babylon[H894] smote them, and slew them at Riblah in the land of Hamath. So Judah was carried away out of their land.

2Ki 25:22 KJV
And [as for] the people that remained in the land of Judah, whom Nebuchadnezzar king of Babylon[H894] had left, even over them he made Gedaliah the son of Ahikam, the son of Shaphan, ruler.

2Ki 25:23 KJV
And when all the captains of the armies, they and their men, heard that the king of Babylon[H894] had made Gedaliah governor, there came to Gedaliah to Mizpah, even Ishmael the son of Nethaniah, and Johanan the son of Careah, and Seraiah the son of Tanhumeth the Netophathite, and Jaazaniah the son of a Maachathite, they and their men.

2Ki 25:24 KJV
And Gedaliah sware to them, and to their men, and said unto them, Fear not to be the servants of the Chaldees: dwell in the land, and serve the king of Babylon;[H894] and it shall be well with you.

2Ki 25:27 KJV
And it came to pass in the seven and thirtieth year of the captivity of Jehoiachin king of Judah, in the twelfth month, on the seven and twentieth [day] of the month, [that] Evilmerodach king of Babylon[H894] in the year that he began to reign did lift up the head of Jehoiachin king of Judah out of prison;

2Ki 25:28 KJV
And he spake kindly to him, and set his throne above the throne of the kings that [were] with him in Babylon;[H894]

1Ch 9:1 KJV
So all Israel were reckoned by genealogies; and, behold, they [were] written in the book of the kings of Israel and Judah, [who] were carried away to Babylon[H894] for their transgression.

2Ch 32:31 KJV
Howbeit in [the business of] the ambassadors of the princes of Babylon,[H894] who sent unto him to enquire of the wonder that was [done] in the land, God left him, to try him, that he might know all [that was] in his heart.

2Ch 33:11 KJV
Wherefore the LORD brought upon them the captains of the host of the king of Assyria, which took Manasseh among the thorns, and bound him with fetters, and carried him to Babylon.[H894]

2Ch 36:6 KJV
Against him came up Nebuchadnezzar king of Babylon,[H894] and bound him in fetters, to carry him to Babylon.[H894]

2Ch 36:7 KJV
Nebuchadnezzar also carried of the vessels of the house of the LORD to Babylon,[H894] and put them in his temple at Babylon.[H894]

2Ch 36:10 KJV
And when the year was expired, king Nebuchadnezzar sent, and brought him to Babylon,[H894] with the goodly vessels of the house of the LORD, and made Zedekiah his brother king over Judah and Jerusalem.

2Ch 36:18 KJV
And all the vessels of the house of God, great and small, and the treasures of the house of the LORD, and the treasures of the king, and of his princes; all [these] he brought to Babylon.[H894]

2Ch 36:20 KJV
And them that had escaped from the sword carried he away to Babylon;[H894] where they were servants to him and his sons until the reign of the kingdom of Persia:

Ezr 1:11 KJV
All the vessels of gold and of silver [were] five thousand and four hundred. All [these] did Sheshbazzar bring up with [them of] the captivity that were brought up from Babylon[H894] unto Jerusalem.

Ezr 2:1 KJV
Now these [are] the children of the province that went up out of the captivity, of those which had been carried away, whom Nebuchadnezzar the king of Babylon[H894] had carried away unto Babylon,[H894] and came again unto Jerusalem and Judah, every one unto his city;

Ezr 7:6 KJV
This Ezra went up from Babylon;[H894] and he [was] a ready scribe in the law of Moses, which the LORD God of Israel had given: and the king granted him all his request, according to the hand of the LORD his God upon him.

Ezr 7:9 KJV
For upon the first [day] of the first month began he to go up from Babylon,[H894] and on the first [day] of the fifth month came he to Jerusalem, according to the good hand of his God upon him.

Ezr 8:1 KJV
These [are] now the chief of their fathers, and [this is] the genealogy of them that went up with me from Babylon,[H894] in the reign of Artaxerxes the king.

Neh 7:6 KJV
These [are] the children of the province, that went up out of the captivity, of those that had been carried away, whom Nebuchadnezzar the king of Babylon[H894] had carried away, and came again to Jerusalem and to Judah, every one unto his city;

Neh 13:6 KJV
But in all this [time] was not I at Jerusalem: for in the two and thirtieth year of Artaxerxes king of Babylon[H894] came I unto the king, and after certain days obtained I leave of the king:

Est 2:6 KJV
Who had been carried away from Jerusalem with the captivity which had been carried away with Jeconiah king of Judah, whom Nebuchadnezzar the king of Babylon[H894] had carried away.

Psa 87:4 KJV
I will make mention of Rahab and Babylon[H894] to them that know me: behold Philistia, and Tyre, with Ethiopia; this [man] was born there.

Psa 137:1 KJV
By the rivers of Babylon,[H894] there we sat down, yea, we wept, when we remembered Zion.

Psa 137:8 KJV
O daughter of Babylon,[H894] who art to be destroyed; happy [shall he be], that rewardeth thee as thou hast served us.

Isa 13:1 KJV
The burden of Babylon,[H894] which Isaiah the son of Amoz did see.

\chapter{Meanings of captivity}

gâlâh, gaw-law'; a primitive root; to denude (especially in a disgraceful sense); by implication, to exile (captives being usually stripped); figuratively, to reveal:— advertise, appear, bewray, bring, (carry, lead, go) captive (into captivity), depart, disclose, discover, exile, be gone, open, × plainly, publish, remove, reveal, × shamelessly, shew, × surely, tell, uncover.

\section{}

Gen 9:21 KJV
And he drank of the wine, and was drunken; and he was uncovered[H1540] within his tent.

Gen 35:7 KJV
And he built there an altar, and called the place Elbethel: because there God appeared[H1540] unto him, when he fled from the face of his brother.

Exo 20:26 KJV
Neither shalt thou go up by steps unto mine altar, that thy nakedness be not discovered[H1540] thereon.

Lev 18:6 KJV
None of you shall approach to any that is near of kin to him, to uncover[H1540] [their] nakedness: I [am] the LORD.

Lev 18:7 KJV
The nakedness of thy father, or the nakedness of thy mother, shalt thou not uncover:[H1540] she [is] thy mother; thou shalt not uncover[H1540] her nakedness.

Lev 18:8 KJV
The nakedness of thy father's wife shalt thou not uncover:[H1540] it [is] thy father's nakedness.

Lev 18:9 KJV
The nakedness of thy sister, the daughter of thy father, or daughter of thy mother, [whether she be] born at home, or born abroad, [even] their nakedness thou shalt not uncover.[H1540]

Lev 18:10 KJV
The nakedness of thy son's daughter, or of thy daughter's daughter, [even] their nakedness thou shalt not uncover:[H1540] for theirs [is] thine own nakedness.

Lev 18:11 KJV
The nakedness of thy father's wife's daughter, begotten of thy father, she [is] thy sister, thou shalt not uncover[H1540] her nakedness.

Lev 18:12 KJV
Thou shalt not uncover[H1540] the nakedness of thy father's sister: she [is] thy father's near kinswoman.

Lev 18:13 KJV
Thou shalt not uncover[H1540] the nakedness of thy mother's sister: for she [is] thy mother's near kinswoman.

Lev 18:14 KJV
Thou shalt not uncover[H1540] the nakedness of thy father's brother, thou shalt not approach to his wife: she [is] thine aunt.

Lev 18:15 KJV
Thou shalt not uncover[H1540] the nakedness of thy daughter in law: she [is] thy son's wife; thou shalt not uncover[H1540] her nakedness.

Lev 18:16 KJV
Thou shalt not uncover[H1540] the nakedness of thy brother's wife: it [is] thy brother's nakedness.

Lev 18:17 KJV
Thou shalt not uncover[H1540] the nakedness of a woman and her daughter, neither shalt thou take her son's daughter, or her daughter's daughter, to uncover[H1540] her nakedness; [for] they [are] her near kinswomen: it [is] wickedness.

Lev 18:18 KJV
Neither shalt thou take a wife to her sister, to vex [her], to uncover[H1540] her nakedness, beside the other in her life [time].

Lev 18:19 KJV
Also thou shalt not approach unto a woman to uncover[H1540] her nakedness, as long as she is put apart for her uncleanness.

Lev 20:11 KJV
And the man that lieth with his father's wife hath uncovered[H1540] his father's nakedness: both of them shall surely be put to death; their blood [shall be] upon them.

Lev 20:17 KJV
And if a man shall take his sister, his father's daughter, or his mother's daughter, and see her nakedness, and she see his nakedness; it [is] a wicked thing; and they shall be cut off in the sight of their people: he hath uncovered[H1540] his sister's nakedness; he shall bear his iniquity.

Lev 20:18 KJV
And if a man shall lie with a woman having her sickness, and shall uncover[H1540] her nakedness; he hath discovered her fountain, and she hath uncovered[H1540] the fountain of her blood: and both of them shall be cut off from among their people.

Lev 20:19 KJV
And thou shalt not uncover[H1540] the nakedness of thy mother's sister, nor of thy father's sister: for he uncovereth his near kin: they shall bear their iniquity.

Lev 20:20 KJV
And if a man shall lie with his uncle's wife, he hath uncovered[H1540] his uncle's nakedness: they shall bear their sin; they shall die childless.

Lev 20:21 KJV
And if a man shall take his brother's wife, it [is] an unclean thing: he hath uncovered[H1540] his brother's nakedness; they shall be childless.

Num 22:31 KJV
Then the LORD opened[H1540] the eyes of Balaam, and he saw the angel of the LORD standing in the way, and his sword drawn in his hand: and he bowed down his head, and fell flat on his face.

Num 24:4 KJV
He hath said, which heard the words of God, which saw the vision of the Almighty, falling [into a trance], but having his eyes open:[H1540]

Num 24:16 KJV
He hath said, which heard the words of God, and knew the knowledge of the most High, [which] saw the vision of the Almighty, falling [into a trance], but having his eyes open:[H1540]

Deu 22:30 KJV
A man shall not take his father's wife, nor discover[H1540] his father's skirt.

Deu 27:20 KJV
Cursed [be] he that lieth with his father's wife; because he uncovereth[H1540] his father's skirt. And all the people shall say, Amen.

Deu 29:29 KJV
The secret [things belong] unto the LORD our God: but those [things which are] revealed[H1540] [belong] unto us and to our children for ever, that [we] may do all the words of this law.

Jdg 18:30 KJV
And the children of Dan set up the graven image: and Jonathan, the son of Gershom, the son of Manasseh, he and his sons were priests to the tribe of Dan until the day of the captivity[H1540] of the land.

Rth 3:4 KJV
And it shall be, when he lieth down, that thou shalt mark the place where he shall lie, and thou shalt go in, and uncover[H1540] his feet, and lay thee down; and he will tell thee what thou shalt do.

Rth 3:7 KJV
And when Boaz had eaten and drunk, and his heart was merry, he went to lie down at the end of the heap of corn: and she came softly, and uncovered[H1540] his feet, and laid her down.

Rth 4:4 KJV
And I thought to advertise[H1540] thee, saying, Buy [it] before the inhabitants, and before the elders of my people. If thou wilt redeem [it], redeem [it]: but if thou wilt not redeem [it, then] tell me, that I may know: for [there is] none to redeem [it] beside thee; and I [am] after thee. And he said, I will redeem [it].

1Sa 2:27 KJV
And there came a man of God unto Eli, and said unto him, Thus saith the LORD, Did I plainly[H1540] appear[H1540] unto the house of thy father, when they were in Egypt in Pharaoh's house?

1Sa 3:7 KJV
Now Samuel did not yet know the LORD, neither was the word of the LORD yet revealed[H1540] unto him.

1Sa 3:21 KJV
And the LORD appeared again in Shiloh: for the LORD revealed[H1540] himself to Samuel in Shiloh by the word of the LORD.

1Sa 4:21 KJV
And she named the child Ichabod, saying, The glory is departed[H1540] from Israel: because the ark of God was taken, and because of her father in law and her husband.

1Sa 4:22 KJV
And she said, The glory is departed[H1540] from Israel: for the ark of God is taken.

1Sa 9:15 KJV
Now the LORD had told[H1540] Samuel in his ear a day before Saul came, saying,

1Sa 14:8 KJV
Then said Jonathan, Behold, we will pass over unto [these] men, and we will discover[H1540] ourselves unto them.

1Sa 14:11 KJV
And both of them discovered[H1540] themselves unto the garrison of the Philistines: and the Philistines said, Behold, the Hebrews come forth out of the holes where they had hid themselves.

1Sa 20:2 KJV
And he said unto him, God forbid; thou shalt not die: behold, my father will do nothing either great or small, but that he will shew[H1540] it me: and why should my father hide this thing from me? it [is] not [so].

1Sa 20:12 KJV
And Jonathan said unto David, O LORD God of Israel, when I have sounded my father about to morrow any time, [or] the third [day], and, behold, [if there be] good toward David, and I then send not unto thee, and shew[H1540] it thee;

1Sa 20:13 KJV
The LORD do so and much more to Jonathan: but if it please my father [to do] thee evil, then I will shew[H1540] it thee, and send thee away, that thou mayest go in peace: and the LORD be with thee, as he hath been with my father.

1Sa 22:8 KJV
That all of you have conspired against me, and [there is] none that sheweth[H1540] me that my son hath made a league with the son of Jesse, and [there is] none of you that is sorry for me, or sheweth[H1540] unto me that my son hath stirred up my servant against me, to lie in wait, as at this day?

1Sa 22:17 KJV
And the king said unto the footmen that stood about him, Turn, and slay the priests of the LORD; because their hand also [is] with David, and because they knew when he fled, and did not shew[H1540] it to me. But the servants of the king would not put forth their hand to fall upon the priests of the LORD.

2Sa 6:20 KJV
Then David returned to bless his household. And Michal the daughter of Saul came out to meet David, and said, How glorious was the king of Israel to day, who uncovered[H1540] himself to day in the eyes of the handmaids of his servants, as one of the vain fellows shamelessly[H1540] uncovereth[H1540] himself!

2Sa 7:27 KJV
For thou, O LORD of hosts, God of Israel, hast revealed[H1540] to thy servant, saying, I will build thee an house: therefore hath thy servant found in his heart to pray this prayer unto thee.

2Sa 15:19 KJV
Then said the king to Ittai the Gittite, Wherefore goest thou also with us? return to thy place, and abide with the king: for thou [art] a stranger, and also an exile.[H1540]

2Sa 22:16 KJV
And the channels of the sea appeared, the foundations of the world were discovered,[H1540] at the rebuking of the LORD, at the blast of the breath of his nostrils.

\chapter{Jehoiachin}

Jehoiachin = "Jehovah establishes"

king of Judah, son of Jehoiakim, and the next to last king of Judah before the Babylonian captivity; kingship lasted for 3 months and 10 days before he surrendered to Nebuchadnezzar who took him to Babylon and imprisoned him for 36 years when he was finally released


\section{}











\end{document}
